Parallel Simulation of Adaptive Random Boolean Networks

### 2016-07-14 Paper/paper.tex
Add the description of Kss and Attr. Dist. To Exp. study

	\paragraph{Rewiring more than one node per epoch.} In order to determine how $N_{rew}$ influences the rate of convergence to a dynamical equilibrium, we performed $1000$ epochs of evolution with $N=1000$ and $N_{rew}=[1, 5]$. The results of these simulations are shown in Figure \ref{fig:nrew}. With increased value of $N_{rew}$ mean connectivity grows faster and the system reaches steady state at approximately 500th epoch for $N_{rew}=5$. We limited the attractor length to $\mu_{max}=10^7$ for these experiments.

	\paragraph{Limiting the maximum attractor length.} Introducing a limit on attractor length leads to a situation when an attractor can not be found. In these cases $N_{rew}$ nodes are rewired according to their activity during the last $\mu_max$ state updates. These states can belong either to a transient period or an attractor. However, the results of our experiments, presented in Tables \ref{table:percentage_of_attractors}, \ref{table:kss}, indicate that low percentage of attractors found does not influence the steady state connectivity obtained as a result of the evolution process.

@@

	\paragraph{Limiting the maximum attractor length.}
	\begin{figure}[ht!]
		\begin{minipage}[t]{0.45\textwidth}
			\includegraphics[width=1.0\textwidth]{plots/evolution}
			\caption{Evolution of mean network connectivity}
		\end{minipage}\hfill
		\begin{minipage}[t]{0.45\textwidth}
			\centering
			\includegraphics[width=1.0\textwidth]{plots/attractors}
			\caption{Empirical distribution of attractor lengths}
		\end{minipage}
	\end{figure}
	%------------------------------------------------------------------------------
	\clearpage
	\section{Conclusion}
	The enormous size of RBN ensemble makes them appropriate to model various complex systems but also raises significant challenges for their numerical investigation. Even a problem of search for a single attractor of RBN is computationally hard for a networks larger than several dozens of nodes because of an exponential growth of a number of iterations with an increase of a network size.

>>>>

	\paragraph{Rewiring more than one node per epoch.} In order to determine how $N_{rew}$ influences the rate of convergence to a dynamical equilibrium, we performed $1000$ epochs of evolution with $N=1000$ and $N_{rew}=[1, 5]$. The results of these simulations are shown in Figure \ref{fig:nrew}. With increased value of $N_{rew}$ mean connectivity grows faster and the system reaches steady state at approximately 500th epoch for $N_{rew}=5$. Therefore, we conclude that by rewiring $N_{rew} > 1$ nodes per epoch one can lower the number of epochs required to reach steady state. We limited the attractor length to $\mu_{max}=10^7$ for these experiments.

	\paragraph{Limiting the maximum attractor length.} Introducing a limit on attractor length leads to a situation when an attractor can not be found. In these cases $N_{rew}$ nodes are rewired according to their activity during the last $\mu_{max}$ state updates. These states can belong to either a transient period or an attractor. However, the results of our experiments, presented in Tables \ref{table:percentage_of_attractors}, \ref{table:kss}, indicate that low percentage of attractors found does not influence the steady state connectivity obtained as a result of the evolution process.

@@

	Using the approaches discussed above we were able perform simulations on networks consisting of up to 1000 nodes. Plots of the evolution of mean in-degree connectivity and the empirical distribution of attractor lengths are shown in Figures \ref{fig:evolution} and \ref{fig:attractors} respectively. The peaks near $\mu=10^7$ in Figure \ref{fig:attractors} are caused by the limit on the attractor length $\mu_{max} = 10^7$.

	\begin{figure}[h]
		\begin{minipage}[t]{0.45\textwidth}
			\includegraphics[width=1.0\textwidth]{plots/evolution}
			\caption{Evolution of mean network connectivity}
			\label{fig:evolution}
		\end{minipage}\hfill
		\begin{minipage}[t]{0.45\textwidth}
			\centering
			\includegraphics[width=1.0\textwidth]{plots/attractors}
			\caption{Empirical distribution of attractor lengths}
			\label{fig:attractors}
		\end{minipage}
	\end{figure}
	%------------------------------------------------------------------------------
	\clearpage
	\section{Conclusion}
	The enormous size of RBN ensemble makes them appropriate to model various complex systems but also raises significant challenges for their numerical investigation. Even a problem of search for a single attractor of RBN is computationally hard for a networks larger than several dozens of nodes because of an exponential growth of a number of iterations with an increase of a network size.
